---
title: "Clustering - Crime dataset"
author: "harsha"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r}
library(readr)
crime_data <- read_csv("D:/Modules/Module 12/crime_data.csv")
View(crime_data)

str(crime_data)

normalized_data<-scale(crime_data[,2:5]) #excluding the university name columnbefore normalizing
View(normalized_data)


d <- dist(normalized_data, method = "euclidean") # distance matrix
d
# Model Building
fit <- hclust(d, method="complete")
View(fit)
fit$labels
fit$dist.method

```{r pressure, echo=FALSE}

plot(fit) # display dendrogram
plot(fit, hang=-1)
groups <- cutree(fit, k=5) # cut tree into 5 clusters
class(groups)
?cutree
rect.hclust(fit, k=5, border="red")
?rect.hclust

membership<-as.matrix(groups)
table(membership)

final <- data.frame(crime_data, membership)
#final <- cbind(mydata, membership)
View(final)
##final1 <- final[,c(ncol(final),1:(ncol(final)-1))]
install.packages("data.table")
library(data.table)
setcolorder(final,c("membership"))
View(final)

```
  


```

